\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-24 2nd report/2report.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta, positioning}

@@

\begin{flushleft}
$
\begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
& \quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*  + \text{remaining 10 terms}\big\}
\end{aligned}
$
\end{flushleft}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
    % 右侧：PT表达式
    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+2^+3^+4^+5^+]=0}\\
        {A_5[1^-2^+3^+4^+5^+]=0}\\
        \textcolor{red}{A_5[1^-2^-3^+4^+5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-3em}
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}
\begin{frame}
    \frametitle{Momentum Shift in BCFW}
    \textbf{What did BCFW do to make the shift?}

@@

    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
   \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    and 
\begin{equation*}
    \mathrm{Res}|_{z=z_I}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
\end{equation*}
\end{frame}

\vspace*{2em}
\textcolor{red}{$\bigstar$ \Large This is the power of BCFW recursion relation.}
\end{frame}
\begin{frame}
\frametitle{Spinor-helicity formalism}
    \begin{itemize}
        \item $\textbf{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation*}
    same for
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
    \begin{equation*}
        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \end{equation*}
    \end{itemize}
\vspace{-2em}
    \begin{itemize}
    \item \textbf{Massive Case}\\
    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{ On-shell 3-point can be completely determined}
    \textbf{On-shell 3-point for real momentum}

\begin{frame}
    \textbf{Another necessarity to introduce complex momentum}

    If the momentum is complexed, we have 
    \begin{equation*}
        \avg{12}\neq[21]^*
    \end{equation*}
    Then we can obtain
    \begin{equation*}
        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
    \end{equation*}
    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
    \begin{equation*}
        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
    \end{equation*}
    Little group scaling tells us that
    \begin{equation*}
        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
    \end{equation*}
    We can obtain
    \begin{equation*}
        2h_1=-x_{12}-x_{13}
    \end{equation*}
    Similarly, we can also obtain
    \begin{equation*}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation*}
\end{frame}

@@

\begin{frame}
    \begin{itemize}
        \item Compact formula for general case
        \begin{equation*}
            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
        \end{equation*} 
        \begin{minipage}{0.7\textwidth}
            \raggedright  % 或者 \centering 或 \raggedleft
            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
            $\star$: \,Order for gauge group 1\\
            $\ast$: \,Order for gauge group 2 
            \end{minipage}

@@

        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{CSW expansion}
    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
    \begin{equation*}
        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
    \end{equation*}
    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.

@@

@@

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\usepackage{tikz}
\usepackage{cancel}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta, positioning}

@@

\begin{flushleft}
$
\begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, (\epsilon_1 \cdot \epsilon_3^*) \, (\epsilon_2 \cdot p_1) \, (\epsilon_4^* \cdot p_3) 
+ 2\, (\epsilon_1 \cdot \epsilon_2) \, (\epsilon_3^* \cdot p_1) \, (\epsilon_4^* \cdot p_3) \\
& \quad - 2\, (\epsilon_1 \cdot p_4) \, (\epsilon_2 \cdot p_1) \, (\epsilon_3^* \cdot \epsilon_4^*)
+ (\epsilon_1 \cdot \epsilon_2) \, (p_4 \cdot p_1) \, (\epsilon_3^* \cdot \epsilon_4^*)  + \text{10 terms}\big\}
\end{aligned}
$
\end{flushleft}

@@

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};
\end{tikzpicture}
\end{center}
\vspace{-1em}
    % 右侧：PT表达式
    \qquad \textbf{Parke–Taylor Formula (MHV amplitudes):}
    \begin{gather*}
        {A_5[1^+2^+3^+4^+5^+]=0}\\
        {A_5[1^-2^+3^+4^+5^+]=0}\\
        \textcolor{red}{A_5[1^-2^-3^+4^+5^+]=\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}\quad (\text{first non-trival one})\\
    \end{gather*}
    \vspace{-3em}
    \begin{gather*}
        {A_5[1^-2^-3^-4^-5^-]=0}\\
        {A_5[1^+2^-3^-4^-5^-]=0}\\
        \textcolor{red}{A_5[1^+2^+3^-4^-5^-]=\frac{[12]^4}{[12][23][34][45][51]}}
    \end{gather*}
\end{frame}

\begin{frame}
    \frametitle{Momentum Shift in BCFW}
    \textbf{What did BCFW do to make the shift?}

@@

\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

\begin{frame}
\frametitle{Little group scaling}
    \begin{itemize}
        \item $\textbf{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation*}
    same for
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling:
    \begin{equation*}
        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \end{equation*}
    \end{itemize}
\vspace{-2em}
    \begin{itemize}
    \item \textbf{Massive Case}\\
    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{ On-shell 3-point can be completely determined}
    \textbf{Another necessarity to introduce complex momentum}
    If the momentum is complexed, we have 
    \begin{equation*}
        \avg{12}\neq[21]^*
    \end{equation*}
    Then we can obtain
    \begin{equation*}
        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
    \end{equation*}
    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
    \begin{equation*}
        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
    \end{equation*}
    Little group scaling tells us that
    \begin{equation*}
        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
    \end{equation*}
    We can obtain
    \begin{equation*}
        2h_1=-x_{12}-x_{13}
    \end{equation*}
    Similarly, we can also obtain
    \begin{equation*}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation*}
\end{frame}

@@

\begin{frame}
    Here I show the concrete computation process 
    \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{6pt.eps}
    \end{figure}
    \vspace{-1em}
    \begin{align*}
    A_1&=\frac{(-1)\asqu{\hat{2}6}\asqu{16}}{\mdavg{25}{56}\!\avg{61}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=\frac{\asqu{26}\avg{16}}{\mdavg{25}{56}\!\mdavg{\hat{2}\hat{I}}{\hat{I}1}}\times\frac{1}{s_{34}}\times\frac{[34]^3}{[4\hat{I}][\hat{I}3]}\notag\\
    &=\frac{\asqu{26}\avg{16}\bcancel{[34]^3}\bcancel{\avg{42}}}{\mdavg{25}{56}\!\mdavg{41}{32}\!\avg{43}\bcancel{[43][43][34]}\bcancel{\avg{24}}}\notag\\
    &=\frac{\asqu{26}\!\asqu{16}}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
    \end{align*}
\end{frame}
\begin{frame}
    \begin{itemize}
        \item Compact formula for general case
        \begin{equation*}
            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
        \end{equation*} 
        \begin{minipage}{0.7\textwidth}
            \raggedright  % 或者 \centering 或 \raggedleft
            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
            $\star$: \,Order for gauge group 1\\
            $\ast$: \,Order for gauge group 2 
            \end{minipage}

@@

        \textcolor{red}{The equivalence between two different shift is related to powerful residue theorem (N. Arkani-Hamed, F. Cachazo, C. Cheung, and J. Kaplan,
        JHEP 1003, 020 (2010) [arXiv:0907.5418 [hep-th]].) and Grassmannian.}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{CSW(Cachazo-Svrcek-Witten) expansion}
    We can also consider a shift that is implemented via a “holomorphic” square-spinor shift:
    \begin{equation*}
        \sket{\hat{i}}=\sket{i}+zc_i\sket{X},\qquad \aket{\hat{i}}=\aket{i}
    \end{equation*}
    Here $\sket{X}$ is an arbitrary reference spinor and the coefficients $c_i$ satisfy $\sum_{i=1}^{n} c_i \aket{i} = 0$.
    %Here we consider the situation where all $c_i\neq 0$, so that all momentum are shifted, called all-line shift.
    \begin{figure}
        \centering
        \includegraphics[width=0.7\textwidth]{NMHV.png}
    \end{figure}
    There are two possibilities: $\mathrm{anti\text{-}MHV_3}(=0)\times \mathrm{NMHV}$ ~or~ $\mathrm{MHV}\times\mathrm{MHV}$.
\end{frame}

\begin{frame}
    For example, the 6pt split NMHV amplitude
    \begin{figure}
        \centering
        \includegraphics[width=1\textwidth]{6ptSpNMHV.png}
    \end{figure}

    \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=1\textwidth]{exNMHV.png}
\end{minipage}
\hfill
\begin{minipage}{0.66\textwidth}
    \centering
    \[
    = \frac{\avg{1\hat{P}_I}^4}{\avg{1\hat{P}_I} \avg{\hat{P}_I 5} \avg{56} \avg{61}}
    \frac{1}{P_{156}^2}
    \frac{\avg{23}^4}{\avg{23} \avg{34} \avg{4\hat{P}_I} \avg{\hat{P}_I 2}} \,.
    \]
\end{minipage}
\pause

We can write 
\begin{equation*}
    \aket{\hat{P}_I}\frac{[\hat{P}_IX]}{[\hat{P}_IX]}=\hat{P}_I\sket{X}\frac{1}{[\hat{P}_IX]}=P_I\sket{X}\frac{1}{[\hat{P}_IX]}
\end{equation*}
\end{frame}
\begin{frame}
    We can use the prescription
    \begin{equation*}
        \aket{\hat{P}_I}\rightarrow P_I \sket{X}
    \end{equation*}
    \begin{minipage}{0.38\textwidth}
    \centering
    \includegraphics[width=\textwidth]{FinalNMHV.png}
\end{minipage}
\hfill
\begin{minipage}{0.62\textwidth}
    \centering
    \[
= \frac{\langle 1|P_{156}|X]^4}{\langle 1|P_{156}|X] \langle 5|P_{156}|X] \langle 56\rangle \langle 61\rangle}
\cdot \frac{1}{P_{156}^2}
\cdot \frac{\langle 23\rangle^4}{\langle 23\rangle \langle 34\rangle \langle 4|P_{156}|X] \langle 2|P_{156}|X]} \,.
\]

\end{minipage}

@@

\begin{frame}
        \textbf{On-shell 3-point for real momentum}

@@

\vspace*{2em}
\textcolor{red}{$\bigstar$ \Large This is the power of BCFW recursion relation.}
\end{frame}
